Probabilistic Catalogs from Crowded Star Fields

### 2012-08-31 paper/ms.tex
CDF
CDF formulae
Inverse of F
Random tweaking

@@

\subsection{The Sampling Distribution}
The sampling distribution is a probabilistic model for the process that
generates the data. {\bf PSF and Gaussian Noise}

@@

@@

\section{Broken Pareto Distribution}

The Broken Pareto (power-law) distribution is:
\begin{eqnarray}
p(x) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
x^{-\alpha_1 - 1} & & x_1 \leq x \leq x_2 \\
x^{-\alpha_2 - 1} & & x > x_2
\end{array}
\right.
.
\end{eqnarray}
With normalising terms included, the proportionality becomes an equality:
\begin{eqnarray}
p(x) &=&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
Z_1^{-1}x^{-\alpha_1 - 1}, & & x_1 \leq x \leq x_2 \\
Z_2^{-1}x^{-\alpha_2 - 1}, & & x > x_2
\end{array}
\right.
.
\end{eqnarray}

>>>>

\abstract{We introduce a fully probabilistic method for producing catalogs
from images of crowded stellar fields. The method is demonstrated on simulated
data where the luminosity function of the stars is a broken power-law.}

@@

\subsection{The Sampling Distribution}
The sampling distribution is a probabilistic model for the process that
generates the data. The pixel-convolved PSF-convolved scene is given by:
\begin{eqnarray}
\mathcal{M}(x, y) &=& \sum_{i=1}^N \mathcal{P}(x - x_i, y - y_i)
\end{eqnarray}
where $\mathcal{P}$ is the pixel-convolved PSF. Throughout this paper we
assume the pixel-convolved PSF is a known mixture of two concentric circular
Gaussians:
\begin{eqnarray}
\mathcal{P}(x, y) &=&
\end{eqnarray}

@@

\section{Broken Power-Law Distribution}
The broken power-law distribution is defined by:
\begin{eqnarray}
p(x) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
x^{-\alpha_1 - 1} & & x_1 \leq x \leq x_2 \\
x^{-\alpha_2 - 1} & & x > x_2
\end{array}
\right.
.
\end{eqnarray}
With normalising terms included, the proportionality becomes an equality:
\begin{eqnarray}
p(x) &=&
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
Z_1^{-1}x^{-\alpha_1 - 1}, & & x_1 \leq x \leq x_2 \\
Z_2^{-1}x^{-\alpha_2 - 1}, & & x > x_2
\end{array}
\right.
.
\end{eqnarray}

The cumulative distribution (CDF) is:
\begin{eqnarray}
P(X \leq x) = F(x) &=& 
\left\{
\begin{array}{lcr}
0, & & x < x_1 \\
(Z_1\alpha_1)^{-1}\left(x_1^{-\alpha_1} - x^{-\alpha_1}\right), & & x_1 \leq x \leq x_2 \\
1 - (Z_2\alpha_2)^{-1}x^{-\alpha_2}, & & x > x_2 
\end{array}
\right.
\end{eqnarray}
and the inverse CDF is:
\begin{eqnarray}
F^{-1}(u) &=& 
\left\{
\begin{array}{lcr}
\left[x_1^{-\alpha_1} - uZ_1\alpha_1\right]^{-1/\alpha_1}, & & 0 < u < 1 - (Z_2\alpha_2)^{-1}x_2^{-\alpha_2}\\
\left[Z_2\alpha_2(1-u)\right]^{-1/\alpha_2},& & 1 - (Z_2\alpha_2)^{-1}x_2^{-\alpha_2}< u < 1
\end{array}
\right.
\end{eqnarray}

@@
